Measuring Subgroup Preferences in Conjoint Experiments\footnote{We thank Benjamin Lauderdale, Jamie Druckman, Yusaku Horiuchi, the editor, and anonymous reviewers for feedback on this manuscript.}

### 2019-04-13 manuscript.Rnw
drop bms examples; update and expand SI

<<data_bms>>=
if (file.exists("data/bms.rds")) {
    bms <- cj_df(rio::import("data/bms.rds"))
} else {
    bms <- cj_df(rio::import("data/ballard-rosa.dta"))

    # setup terms
    bms$taxrate1 <- factor(rio::characterize(bms$taxrate1),
                           levels = c("0%", "5%", "15%", "25%"),
                           labels = c("<10k: 0%", "<10k: 5%", "<10k: 15%", "<10k: 25%"))
    bms$taxrate2 <- factor(rio::characterize(bms$taxrate2),
                           levels = c("5%", "15%", "25%", "35%"),
                           labels = c("10-35k: 5%", "10-35k: 15%", "10-35k: 25%", "10-35k: 35%"))
    bms$taxrate3 <- factor(rio::characterize(bms$taxrate3),
                           levels = c("5%", "15%", "25%", "35%"),
                           labels = c("35-85k: 5%", "35-85k: 15%", "35-85k: 25%", "35-85k: 35%"))
    bms$taxrate4 <- factor(rio::characterize(bms$taxrate4),
                           levels = c("5%", "15%", "25%", "35%"),
                           labels = c("85-175k: 5%", "85-175k: 15%", "85-175k: 25%", "85-175k: 35%"))
    bms$taxrate5 <- factor(rio::characterize(bms$taxrate5),
                           levels = c("5%", "15%", "25%", "35%", "45%"),
                           labels = c("175-375k: 5%", "175-375k: 15%", "175-375k: 25%", "175-375k: 35%", "175-375k: 45%"))
    bms$taxrate6 <- factor(rio::characterize(bms$taxrate6),
                           levels = c("5%", "15%", "25%", "35%", "45%", "55%"),
                           labels = c(">375k: 5%", ">375k: 15%", ">375k: 25%", ">375k: 35%", ">375k: 45%", ">375k: 55%"))
    bms$taxrev <- factor(rio::characterize(bms$taxrev),
                         levels = rev(c("Much more revenue (>125%)",
                                        "More revenue (105-125%)",
                                        "About the same revenue (95-105%)",
                                        "Less revenue (75-95%)",
                                        "Much less revenue (<75%)")),
                         labels = c("<75%", "75-95%", "95-105%", "105-125%", ">125%"))

    # subset variables
    bms <- bms[c("chose_plan", "taxrate1", "taxrate2", "taxrate3", "taxrate4", "taxrate5", "taxrate6", "taxrev",
                 "ineq_averse_dum", "hh_income", "taxes_harm_econ", "work_vs_luck", "race", "above_avg_racial_resentment",
                 "repub_7pt", "democ_7pt", "indep_7pt", "ID", "weight", "saw_revenue")]

    # subset (according to original do file)
    bms <- bms[bms$saw_revenue == 1,]

    # label
    attr(bms$taxrate1, "label") <- "Tax rate for <$10,000"
    attr(bms$taxrate2, "label") <- "Tax rate for $10,000-$35,000"
    attr(bms$taxrate3, "label") <- "Tax rate for $25,000-$85,000"
    attr(bms$taxrate4, "label") <- "Tax rate for $85,000-$175,000"
    attr(bms$taxrate5, "label") <- "Tax rate for $175,000-$375,000"
    attr(bms$taxrate6, "label") <- "Tax rate for >$375,000"
    attr(bms$taxrev, "label") <- "Tax revenue"

    # export
    rio::export(bms, "data/bms.rds")
}
bms$taxes_harm_split <- factor(ifelse(bms$taxes_harm_econ == 1, "Help", ifelse(bms$taxes_harm_econ == 2, "Harm", NA)))
@

@@

As we will show, where preferences in subgroups toward the experimental reference category are similar, the difference-in-AMCEs conveys preferences reasonably well. The problem occurs when preferences between subgroups diverge in the reference category. Here, the difference-in-AMCEs is a misleading representation of underlying patterns of favorability. Given most published conjoint studies report results based upon reference categories chosen for \textit{substantive} reasons about the nature or meaning of the levels rather than the configuration of preferences revealed in the experiment, difference-in-AMCEs should not be assumed to be interpretable as differences in subgroup preferences. The root of this error is likely familiar to many researchers: it is simply a matter of regression specification for models involving interactions between categorical regressors. \citet{EgamiImai2018}, for example, provide an extensive discussion of the implications of this property for interpreting causal interactions between randomized features of conjoint profiles. The state of the published literature would suggest the problem remains non-obvious when applied to descriptive analysis of subgroups in conjoint designs.

@@

\noindent These examples make clear that despite the \textit{causal} inference potentially provided by the AMCE, the quantity of interest is frequently used to provide a characterization of a preferences that has a distinctly descriptive flavor about the relative \textit{levels} of support across profiles and also across subgroups of respondents. Indeed, this style of description is widespread in conjoint analyses. This use of conjoints to provide descriptive inferences about patterns of preferences is important because AMCEs are defined as \textit{relative} quantities, requiring that patterns of preferences are expressed against a baseline, reference category for each conjoint feature. A positive AMCE is read as higher favorability but it is only higher relative to whatever category serves as the baseline. For example, in the \citeauthor{HainmuellerHopkinsYamamoto2014} candidate example, choosing a non-religious candidate as a baseline and interpreting the resulting AMCES means that the differences between other pairs of marginal means (e.g., evaluations of Mormon and Evangelical candidates) are not obvious. The negative direction, and the size, of the AMCEs for Mormon and Evangelical candidates would be different if the least-liked category of Mormons were the reference group. More trivially, \citet{TeeleKallaRosenbluth2018} describe their comparisons about public preferences for female candidates relative to male candidates, but could have equivalent described patterns of equal size but opposite sign comparing preferences over male relative to female candidates.

<<reference_category, dependson=c("data_hainmueller_immigration"), fig.width=8, fig.height=4, fig.cap="Estimated AMCEs for Levels of the `Education' Feature for Each Possible Reference Category from Hainmueller et al.'s (2014) Immigration Experiment">>=
tmp <- amce_by_reference(hainmueller_immigration, ChosenImmigrant ~ Education, ~ Education, id = ~CaseID)
ggplot(tmp, aes(x = estimate, y = level, group = BY, colour = BY)) +
  geom_vline(xintercept = 0, colour = "gray") +
  geom_point(position = ggstance::position_dodgev(height = 1)) +
  geom_errorbarh(aes(xmin = lower, xmax = upper),  
                 size = 0.2, height = 0,
                 position = ggstance::position_dodgev(height = 1)) + 
  scale_colour_discrete(
    guide = ggplot2::guide_legend(
      title = "Reference Category",
      title.position = "top",
      ncol = 2
    )
  ) +
  scale_x_continuous(limits = c(-.3,.3), oob = scales::rescale_none) +
  ylab("") +
  xlab("Estimated AMCE") + 
  theme_minimal() + 
  ggplot2::theme(
    legend.position = "bottom",
    panel.grid.major = ggplot2::element_blank(),
    panel.grid.minor = ggplot2::element_blank()
  )
rm(tmp)
@

% DECIDE WHETHER TO KEEP THIS (AND FIGURE 2):

Though seemingly arbitrary, the choice of reference category for estimating AMCEs can be quite consequential.\footnote{Since this manuscript has been under review, we have been made aware of one working paper by \citet{ClaytonFerwerdaHoriuchi2018}, on the topic of immigration preferences, that correctly notes the need to address the arbitrary reference category in order to compare subgroup preferences.} For example, in \citeauthor{HainmuellerHopkinsYamamoto2014}'s candidate experiment (again, see \ref{fig:hainmueller_candidate_replication}), the least liked education level (``no formal education'') is chosen as a reference category, but the authors could have presented the results using any of the categories as the baseline. Figure \ref{fig:reference_category} shows how the estimated AMCEs for each level of the education feature would have differed depending on that choice. Selecting a reference category that receives middling support (i.e., more favorability than some other feature levels but less favorability than others), makes some AMCEs positive and others negative but all AMCEs can be made positive (or negative) simply by choosing a different baseline. The results would be numerically equivalent --- the alternative linear models used to the estimate the AMCEs have a mathematical equivalence --- but the choice has sizeable consequences for the interpretation of conjoint analyses, as we discuss below.\footnote{In \textit{constrained} conjoint designs, the choice of reference category is even more important. Consider, for example, the design of \citeauthor{HainmuellerHopkinsYamamoto2014}'s immigration experiment, which constrains the ``Country of Origin`` feature so that levels `India,' `Germany,' `France,' `Mexico,' `Philippines,' and `Poland' cannot co-occur with the `Escape Persecution' level of the ``Reason for Application'' feature. Consequently, the AMCE for the ``Escape Persecution'' level (relative to the  ``Reunite with family'' reference category) is only defined for the subset of the design involving countries `China,' `Sudan,' `Somalia,' and `Iraq.' The AMCEs for those four countries (relative to India as a baseline) marginalize across all reasons for application, but the AMCEs for the first six countries marginalize only across the latter two reasons. Thus the interpretation of AMCEs --- and the basic ability to estimate them in constrained designs --- depends entirely upon the selection of a reference category where all feature levels can co-occur. In a design where \textit{all} features are constrained, then AMCEs are undefined for the design as a whole and only estimable for subsets of the design that are \textit{conditionally} unconstrained.}

%To demonstrate this, Figure \ref{fig:reference_category} shows the estimated AMCEs for the country of origin feature from \citeauthor{HainmuellerHopkinsYamamoto2014}'s immigration experiment, with the analysis repeated ten times each time using a different country as the reference category. For example, the top-most set of points and error bars convey the AMCE for Iraq from each of these analyses. When Iraq is the reference category, its AMCE is undefined. When any other country is chosen as a reference category, the AMCE for Iraq is negative because respondents are more negative toward Iraqi immigrants than they are toward those of other countries. Similarly, the bottom set of points and error bars reflects the estimated AMCEs for Germany. When Germany is the reference category, its AMCE is undefined but when any other country is used as the reference category, its AMCE is positive.

%These cases are therefore not \textit{directionally} sensitive to the choice of reference category but of course the point estimates vary considerably. But the estimated AMCE of countries who are neither strongly disliked or strongly favored by respondents are highly sensitive to choice of reference category. Consider, for example, the estimated AMCEs for China (the four set of points from the top). When highly disliked countries are chosen as the reference category (like Somalia, Sudan, or Iraq), the AMCE for China is positive; when highly favored countries are chosen (like Germany, Poland, or the Philippines), the AMCE for China is negative.

@@

<<tkr_replication, dependson=c("data_tkr"), fig.height=4.5, fig.width=5, fig.cap="Replication of Results for `Candidate Sex' Feature from Teele et al. (2018) Candidate Experiment using Full Sample and Subgroup AMCEs and MMs", fig.show="hold", message=FALSE>>=
a <- plot(
  subset(cj(
   tkr, 
   winner ~ feature_sex + feature_experience + feature_marital + feature_job + feature_children + feature_age,
   id = ~ responseid,
   estimate = "amce",
  ), feature == "Candidate Sex"), 
  xlab = NULL, feature_headers = FALSE, vline = 0, xlim = c(-0.11, 0.11), size = 2
) + 
  ggtitle(NULL, "Full Sample AMCEs") + 
  scale_colour_manual("Feature", limits = "Candidate Sex", values = "black") +
  theme(
  	legend.position = "none",
  	panel.border = element_blank(),
  	axis.line.x = element_blank(),
	axis.line.y = element_blank()
  )

b <- plot(
  subset(cj(
   tkr, 
   winner ~ feature_sex + feature_experience + feature_marital + feature_job + feature_children + feature_age,
   id = ~ responseid,
   estimate = "mm",
  ), feature == "Candidate Sex"),
  xlab = NULL, feature_headers = FALSE, vline = 0.5, xlim = c(0.39,0.61), size = 2
) + 
  ggtitle(NULL, "Full Sample MMs") + 
  scale_colour_manual("Feature", limits = "Candidate Sex", values = "black") +
  theme(
   	legend.position = "none",
   	panel.border = element_blank(),
   	axis.line.x = element_blank(),
	axis.line.y = element_blank()
  )

c <- plot(
  subset(cj(
   tkr, 
   winner ~ feature_sex + feature_experience + feature_marital + feature_job + feature_children + feature_age,
   id = ~ responseid,
   estimate = "amce",
   by = ~ PartyID
  ), feature == "Candidate Sex"), 
  xlab = NULL, feature_headers = FALSE, vline = 0, group = "PartyID", xlim = c(-0.11, 0.11), size = 2
) + 
 annotate("text", y = 1.65, x = -0.04, label = "Republicans", size = 3) + 
 annotate("text", y = 1.3, x = 0.05, label = "Democrats", size = 3) + 
 ggtitle(NULL, "Subgroup AMCEs") + 
 scale_colour_manual(values=rep("black", 2)) +
 aes(shape = PartyID) + 
 scale_shape_manual("PartyID", limits = c("Democrat", "Republican"), values = c(15,17)) +
 theme(
   legend.position = "none",
   panel.border = element_blank(),
   axis.line.x = element_blank(),
   axis.line.y = element_blank()
 )

d <- plot(
  subset(cj(
   tkr, 
   winner ~ feature_sex + feature_experience + feature_marital + feature_job + feature_children + feature_age,
   id = ~ responseid,
   estimate = "mm",
   by = ~ PartyID
  ), feature == "Candidate Sex"),
  xlab = NULL, feature_headers = FALSE, vline = 0.5, group = "PartyID", xlim = c(0.39,0.61), size = 2
) + 
 ggtitle(NULL, "Subgroup MMs") + 
 scale_colour_manual(values=rep("black", 2)) +
 aes(shape = PartyID) + 
 scale_shape_manual("PartyID", limits = c("Democrat", "Republican"), values = c(15,17)) +
 theme(
  legend.position = "none",
  panel.border = element_blank(),
  axis.line.x = element_blank(),
  axis.line.y = element_blank()
 )

@@

To draw this example out more fully, the upper panel of Figure \ref{fig:tkr_replication} shows AMCEs for \citeauthor{TeeleKallaRosenbluth2018}'s candidate choice experiment for the full sample of respondents. The second panel shows full sample marginal means. Respondents' preference for female candidates is very apparent in both forms of analysis in the upper two panels because the AMCE definitionally equals the difference in marginal means. But how do Republicans and Democrats differ in their preferences over male and female candidates? The third panel shows conditional AMCEs separately for Democratic and Republican voters, as provided in the original paper and the lower panel shows the results using conditional marginal means for Democratic and Republican voters.\footnote{We opt here for visual presentation of results; tabular presentation of AMCEs, marginal means, and associated standard errors for all examples are included in the Appendix.} By requiring a reference category fixed to zero, the conditional AMCE results in the third panel suggest that there is a very large difference in favorability toward female candidates between Republican and Democratic respondents. In reality, however, the difference in these conditional AMCEs (0.086) reflects the true difference in favorability toward female candidates (difference: 0.045; Democrats: 0.537, Republicans: 0.492) \textit{plus} the difference in favorability toward male candidates (difference: 0.045; Democrats: 0.463, Republicans: 0.508). Because Democrats and Republicans actually differ in their views of profiles containing the reference (male) category, AMCEs sum the true differences in preferences for a given feature level with the difference in preferences toward the reference category.\footnote{Another example that clearly demonstrates the discrepancy between the differences in preferences and the differences in conditional AMCEs can be seen very clearly in the ``political experience'' feature of this experiment (see Supporting Materials). The conditional AMCEs correctly convey that both Democrats and Republicans are more likely to favor experienced than inexperienced candidates. Reading the AMCEs descriptively, however, would suggest that Democratic voters are more favorable toward candidates with all levels of experience compared to Republican voters (i.e., Republicans and Democrats differ in their preferences over experienced candidates). In reality, however, the conditional marginal means reveal that actually Democrats and Republicans have very similar preferences toward candidates with 1 or 3 years of experience, but differ dramatically in their preferences over candidates with no experience (the reference category) and those with 8 years experience. Democrats are much more sensitive to experience than are Republicans and important differences in preferences between the groups are apparent for very high and very low experience, but the conditional AMCEs suggest that preferences differ at all levels of experience, when in reality they do not.}

<<bechtel_difference_comparison, dependson=c("data_bms"), fig.width=8, fig.height=3, fig.cap="True Difference in Favorability and Implied Preference Differences between High and Low Environmentalism Respondents for `Monthly Cost' Feature from Bechtel and Scheve (2013) Climate Agreement Experiment for Each Possible Reference Category">>=
# reported results
main <- cj(bechtel[!is.na(bechtel$environmentalism),], choice_cj ~ cost_cj, id = ~ ID, weights = ~weight, estimate = "amce_diff", by = ~ environmentalism)
main$statistic <- "Originally Reported Difference"
## fill in baseline difference
main[5L, ] <-  main[4L, ]
main[5L, "level"] <- levels(bechtel$cost_cj)[1L]
main[5L, c("estimate", "std.error", "z", "p", "lower", "upper")] <- c(0, rep(NA, 5))

@@

It is worth highlighting two further features in Figure \ref{fig:bechtel_difference_comparison}. First, the alternative differences-in-AMCEs estimates vary mechanically around the difference in marginal means, as the reference category varies (just as the AMCE estimates did in Figure \ref{fig:reference_category}). The difference between marginal means for two groups are always fixed in the data, so the differencing of subgroup AMCEs is merely an exercise is centering those differences at arbitrary points along the range of observed differences in marginal means. Differences-in-AMCEs for a given feature level must therefore necessarily sometimes be positive and sometimes be negative, depending on the reference category used in estimating them. The direction of the difference per se conveys no information about underlying pattern of preferences in the two groups.

@@

\section*{Improved Analysis of Subgroup Preferences in Conjoint Designs}\label{sec:marginalmeans}

@@

We have shown that subgroup analyses of conjoint designs frequently entail the use of difference-in-AMCE comparisons and we have also shown that such analyses, perhaps counterintuitively, do not demonstrate differences in preferences between groups due the near-impossibility of selecting a non-arbitrary reference category against which to estimate AMCEs. Thus the choice of reference category --- while seemingly irrelevant --- has dramatic inferential consequences in conjoint analyses. Here we provide a more complete example, demonstrating the full extent of this problem for interpretation of conjoint results and present alternative forms of analysis that more robustly convey subgroup preferences and the differences (if any) between them. Specifically, we show how reference category changes can lead to visual patterns of differences-in-AMCEs that provide strikingly different interpretations. We then show how to visualize and formally compare subgroup marginal means using simple means comparisons tests to avoid this problem. Finally, we demonstrate how to use nested model comparison tests to formally test for omnibus differences between groups.

Consider the left and right facets of Figure \ref{fig:hainmueller_subgroup_example_plot}, which show the exact same analysis (comparing AMCEs for high and low ethnocentrism respondents) on the same experimental data from \citeauthor{HainmuellerHopkinsYamamoto2014}'s immigration experiment. In panel ``A'' (left), all features are configured so that the reference category is the one with the largest difference in preferences between the two subgroups. In panel ``B'' (right), all features are configured so that the reference category is the one with the smallest difference in preferences between the two subgroups.\footnote{The appendix contains comparable plots for experiments by \citet{BallardRosaMartinScheve2016} and \citet{TeeleKallaRosenbluth2018}.}

@@

\begin{enumerate}
\item Always report unadjusted marginal means when attempting to provide a \textit{descriptive} summary of respondent preferences in addition to , or instead of, AMCEs.\footnote{Like the presentation of AMCEs, displaying marginal means in constrained conjoint designs may also distort apparent patterns given that not all features can co-occur. Partitioning the design into fractions such that each fraction contains a fully unconstrained design would mitigate any concern with that presentation.}

\item Exercise caution when explicitly, or implicitly, interpreting differences-in-AMCEs across subgroups. Differences-in-AMCEs are differences in effect sizes for subgroups, not statments about the relative favorability of the subgroups toward profiles with a feature. Heterogeneous effects do not necessarily mean different underlying preferences. If differences in AMCEs are reported, the choice of reference categories should be discussed explicitly and diagnostics should be provided to justify it.

@@

>>>>

@@

As we will show, where preferences in subgroups toward the experimental reference category are similar, the difference-in-AMCEs conveys preferences reasonably well. The problem occurs when preferences between subgroups diverge in the reference category. Here, the difference-in-AMCEs is a misleading representation of underlying patterns of favorability. Given most published conjoint studies report results based upon reference categories chosen for \textit{substantive} reasons about the nature or meaning of the levels rather than the configuration of preferences revealed in the experiment, difference-in-AMCEs should not be assumed to be interpretable as differences in subgroup preferences. The root of this error is likely familiar to many researchers: it is simply a matter of regression specification for models involving interactions between categorical regressors. \citet{EgamiImai2018}, for example, provide an extensive discussion of the implications of this property for interpreting causal interactions between randomized features of conjoint profiles. The state of the published literature would suggest the problem remains non-obvious when applied to descriptive analysis of subgroups in conjoint designs.\footnote{Since this manuscript has been under review, we have been made aware of one working paper by \citet{ClaytonFerwerdaHoriuchi2018}, on the topic of immigration preferences, that correctly notes the need to address the arbitrary reference category in order to compare subgroup preferences.}

@@

\noindent These examples make clear that despite the \textit{causal} inference potentially provided by the AMCE, the quantity of interest is frequently used to provide a characterization of a preferences that has a distinctly descriptive flavor about the relative \textit{levels} of support across profiles and also across subgroups of respondents. Indeed, this style of description is widespread in conjoint analyses. This use of conjoints to provide descriptive inferences about patterns of preferences is important because AMCEs are defined as \textit{relative} quantities, requiring that patterns of preferences are expressed against a baseline, reference category for each conjoint feature. A positive AMCE is read as higher favorability but it is only higher relative to whatever category serves as the baseline. For example, in the \citeauthor{HainmuellerHopkinsYamamoto2014} candidate example, choosing a non-religious candidate as a baseline and interpreting the resulting AMCES means that the differences between other pairs of marginal means (e.g., evaluations of Mormon and Evangelical candidates) are not obvious. The negative direction, and the size, of the AMCEs for Mormon and Evangelical candidates would be different if the least-liked category of Mormons were the reference group. More trivially, \citet{TeeleKallaRosenbluth2018} describe their comparisons about public preferences for female candidates relative to male candidates, but could have equivalent described patterns of equal size but opposite sign comparing preferences over male relative to female candidates. Appendix \ref{app:referencecategory} includes some additional illustrations of this point for interested readers.

@@

@@

<<tkr_replication, dependson=c("data_tkr"), fig.height=4.5, fig.width=5, fig.cap="Replication of Results for `Candidate Sex' Feature from Teele et al. (2018) Candidate Experiment using Full Sample and Subgroup AMCEs and MMs", fig.show="hold", message=FALSE>>=
a <- plot(
  subset(cj(
   tkr, 
   winner ~ feature_sex,
   id = ~ responseid,
   estimate = "amce",
  ), feature == "Candidate Sex"), 
  xlab = NULL, feature_headers = FALSE, vline = 0, xlim = c(-0.11, 0.11), size = 2
) + 
  ggtitle(NULL, "Full Sample AMCEs") + 
  scale_colour_manual("Feature", limits = "Candidate Sex", values = "black") +
  theme(
  	legend.position = "none",
  	panel.border = element_blank(),
  	axis.line.x = element_blank(),
	axis.line.y = element_blank()
  )

b <- plot(
  subset(cj(
   tkr, 
   winner ~ feature_sex,
   id = ~ responseid,
   estimate = "mm",
  ), feature == "Candidate Sex"),
  xlab = NULL, feature_headers = FALSE, vline = 0.5, xlim = c(0.39,0.61), size = 2
) + 
  ggtitle(NULL, "Full Sample MMs") + 
  scale_colour_manual("Feature", limits = "Candidate Sex", values = "black") +
  theme(
   	legend.position = "none",
   	panel.border = element_blank(),
   	axis.line.x = element_blank(),
	axis.line.y = element_blank()
  )

c <- plot(
  subset(cj(
   tkr, 
   winner ~ feature_sex,
   id = ~ responseid,
   estimate = "amce",
   by = ~ PartyID
  ), feature == "Candidate Sex"), 
  xlab = NULL, feature_headers = FALSE, vline = 0, group = "PartyID", xlim = c(-0.11, 0.11), size = 2
) + 
 annotate("text", y = 1.65, x = -0.04, label = "Republicans", size = 3) + 
 annotate("text", y = 1.3, x = 0.05, label = "Democrats", size = 3) + 
 ggtitle(NULL, "Subgroup AMCEs") + 
 scale_colour_manual(values=rep("black", 2)) +
 aes(shape = PartyID) + 
 scale_shape_manual("PartyID", limits = c("Democrat", "Republican"), values = c(15,17)) +
 theme(
   legend.position = "none",
   panel.border = element_blank(),
   axis.line.x = element_blank(),
   axis.line.y = element_blank()
 )

d <- plot(
  subset(cj(
   tkr, 
   winner ~ feature_sex,
   id = ~ responseid,
   estimate = "mm",
   by = ~ PartyID
  ), feature == "Candidate Sex"),
  xlab = NULL, feature_headers = FALSE, vline = 0.5, group = "PartyID", xlim = c(0.39,0.61), size = 2
) + 
 ggtitle(NULL, "Subgroup MMs") + 
 scale_colour_manual(values=rep("black", 2)) +
 aes(shape = PartyID) + 
 scale_shape_manual("PartyID", limits = c("Democrat", "Republican"), values = c(15,17)) +
 theme(
  legend.position = "none",
  panel.border = element_blank(),
  axis.line.x = element_blank(),
  axis.line.y = element_blank()
 )

To draw this example out more fully, the upper panel of Figure \ref{fig:tkr_replication} shows AMCEs for \citeauthor{TeeleKallaRosenbluth2018}'s candidate choice experiment for the full sample of respondents. The second panel shows full sample marginal means. Respondents' preference for female candidates is very apparent in both forms of analysis in the upper two panels because the AMCE definitionally equals the difference in marginal means. But how do Republicans and Democrats differ in their preferences over male and female candidates? The third panel shows conditional AMCEs separately for Democratic and Republican voters, as provided in the original paper and the lower panel shows the results using conditional marginal means for Democratic and Republican voters.\footnote{We opt here for visual presentation of results; tabular presentation of AMCEs, marginal means, and associated standard errors for all examples are included in the Appendix.} By requiring a reference category fixed to zero, the conditional AMCE results in the third panel suggest that there is a very large difference in favorability toward female candidates between Republican and Democratic respondents. In reality, however, the difference in these conditional AMCEs (0.089) reflects the true difference in favorability toward female candidates (difference: 0.045; Democrats: 0.537, Republicans: 0.492) \textit{plus} the difference in favorability toward male candidates (difference: 0.045; Democrats: 0.463, Republicans: 0.508). Because Democrats and Republicans actually differ in their views of profiles containing the reference (male) category, AMCEs sum the true differences in preferences for a given feature level with the difference in preferences toward the reference category.\footnote{Another example that clearly demonstrates the discrepancy between the differences in preferences and the differences in conditional AMCEs can be seen very clearly in the ``political experience'' feature of this experiment (see Appendix \ref{app:tkrpolexperience}).}

<<bechtel_difference_comparison, dependson=c("data_bms"), fig.width=7.5, fig.height=3, fig.cap="True Difference in Favorability and Implied Preference Differences between High and Low Environmentalism Respondents for `Monthly Cost' Feature from Bechtel and Scheve (2013) Climate Agreement Experiment for Each Possible Reference Category">>=
# reported results
main <- cj(bechtel[!is.na(bechtel$environmentalism),], choice_cj ~ cost_cj, id = ~ ID, weights = ~weight, estimate = "amce_diff", by = ~ environmentalism)
main$statistic <- "Originally Reported Difference"
## fill in baseline difference
main[5L, ] <-  main[4L, ]
main[5L, "level"] <- levels(bechtel$cost_cj)[1L]
main[5L, c("estimate", "std.error", "z", "p", "lower", "upper")] <- c(0, rep(NA, 5))

@@

It is worth highlighting two further features in Figure \ref{fig:bechtel_difference_comparison}. First, the alternative differences-in-AMCEs estimates vary mechanically around the difference in marginal means, as the reference category varies. The difference between marginal means for two groups are always fixed in the data, so the differencing of subgroup AMCEs is merely an exercise is centering those differences at arbitrary points along the range of observed differences in marginal means. Differences-in-AMCEs for a given feature level must therefore necessarily sometimes be positive and sometimes be negative, depending on the reference category used in estimating them. The direction of the difference per se conveys no information about underlying pattern of preferences in the two groups.

@@

\section*{Improved Subgroup Analyses in Conjoint Designs}\label{sec:marginalmeans}

@@

Researchers and consumers of conjoints can avoid the inferential errors that accompany conditional AMCEs by focusing attention on (subgroup) marginal means, differences between subgroup marginal means to infer subgroup differences in preferences toward particular features, and omnibus nested model comparisons to infer subgroup differences across many features. To demonstrate each of these three techniques

Here we provide a more complete example, demonstrating the full extent of this problem for interpretation of conjoint results and present alternative forms of analysis that more robustly convey subgroup preferences and the differences (if any) between them. Specifically, we show how reference category changes can lead to visual patterns of differences-in-AMCEs that provide strikingly different interpretations. We then show how to visualize and formally compare subgroup marginal means using simple means comparisons tests to avoid this problem. Finally, we demonstrate how to use nested model comparison tests to formally test for omnibus differences between groups.

Consider the left and right facets of Figure \ref{fig:hainmueller_subgroup_example_plot}, which show the exact same analysis (comparing AMCEs for high and low ethnocentrism respondents) on the same experimental data from \citeauthor{HainmuellerHopkinsYamamoto2014}'s immigration experiment. In panel ``A'' (left), all features are configured so that the reference category is the one with the largest difference in preferences between the two subgroups. In panel ``B'' (right), all features are configured so that the reference category is the one with the smallest difference in preferences between the two subgroups.\footnote{The appendix contains comparable plots for experiments by \citet{BechtelScheve2013} and \citet{TeeleKallaRosenbluth2018}.}

@@

\begin{enumerate}
\item Always report unadjusted marginal means when attempting to provide a \textit{descriptive} summary of respondent preferences in addition to, or instead of, AMCEs.\footnote{Like the presentation of AMCEs, displaying marginal means in constrained conjoint designs may also distort apparent patterns given that not all features can co-occur. Partitioning the design into fractions such that each fraction contains a fully unconstrained design would mitigate any concern with that presentation.}

\item Exercise caution when explicitly, or implicitly, interpreting differences-in-AMCEs across subgroups. Differences-in-AMCEs are differences in effect sizes for subgroups, not statments about the relative favorability of the subgroups toward profiles with a given feature. Heterogeneous effects do not necessarily mean different underlying preferences. If differences in AMCEs are reported, the choice of reference categories should be discussed explicitly and diagnostics should be provided to justify it.

@@

\section{Impact of Reference Category Choice on AMCEs}\label{app:referencecategory}

Though seemingly arbitrary, the choice of reference category for estimating AMCEs can be quite consequential. For example, in \citeauthor{HainmuellerHopkinsYamamoto2014}'s candidate experiment (again, see \ref{fig:hainmueller_candidate_replication}), the least liked education level (``no formal education'') is chosen as a reference category, but the authors could have presented the results using any of the categories as the baseline.

The figure below shows how the estimated AMCEs for each level of the education feature would have differed depending on that choice. Selecting a reference category that receives middling support (i.e., more favorability than some other feature levels but less favorability than others), makes some AMCEs positive and others negative but all AMCEs can be made positive (or negative) simply by choosing a different baseline. The results would be numerically equivalent --- the alternative linear models used to the estimate the AMCEs have a mathematical equivalence --- but the choice has sizeable consequences for the interpretation of conjoint analyses, as we discuss below.

<<reference_category, dependson=c("data_hainmueller_immigration"), fig.width=8, fig.height=4, fig.cap="", fig.pos="h">>=
tmp <- amce_by_reference(hainmueller_immigration, ChosenImmigrant ~ Education, ~ Education, id = ~CaseID)
ggplot(tmp, aes(x = estimate, y = level, group = BY, colour = BY)) +
  geom_vline(xintercept = 0, colour = "gray") +
  geom_point(position = ggstance::position_dodgev(height = 1)) +
  geom_errorbarh(aes(xmin = lower, xmax = upper),  
                 size = 0.2, height = 0,
                 position = ggstance::position_dodgev(height = 1)) + 
  scale_colour_discrete(
    guide = ggplot2::guide_legend(
      title = "Reference Category",
      title.position = "top",
      ncol = 2
    )
  ) +
  scale_x_continuous(limits = c(-.3,.3), oob = scales::rescale_none) +
  ylab("") +
  xlab("Estimated AMCE") + 
  theme_minimal() + 
  ggplot2::theme(
    legend.position = "bottom",
    panel.grid.major = ggplot2::element_blank(),
    panel.grid.minor = ggplot2::element_blank()
  )
rm(tmp)
@

In \textit{constrained} conjoint designs, the choice of reference category is even more important. Consider, for example, the design of \citeauthor{HainmuellerHopkinsYamamoto2014}'s immigration experiment, which constrains the ``Country of Origin`` feature so that levels `India,' `Germany,' `France,' `Mexico,' `Philippines,' and `Poland' cannot co-occur with the `Escape Persecution' level of the ``Reason for Application'' feature. Consequently, the AMCE for the ``Escape Persecution'' level (relative to the  ``Reunite with family'' reference category) is only defined for the subset of the design involving countries `China,' `Sudan,' `Somalia,' and `Iraq.' The AMCEs for those four countries (relative to India as a baseline) marginalize across all reasons for application, but the AMCEs for the first six countries marginalize only across the latter two reasons. Thus the interpretation of AMCEs --- and the basic ability to estimate them in constrained designs --- depends entirely upon the selection of a reference category where all feature levels can co-occur. In a design where \textit{all} features are constrained, then AMCEs are undefined for the design as a whole and only estimable for subsets of the design that are \textit{conditionally} unconstrained.

\section{Re-analysis of `Political Experience' Feature from Teele et al. (2018)}\label{app:tkrpolexperience}

<<tkr_replication_experience, dependson=c("data_tkr"), fig.height=6, fig.width=7, fig.show="hold", fig.pos="h", message=FALSE>>=
a <- plot(
  subset(cj(
   tkr, 
   winner ~ feature_experience,
   id = ~ responseid,
   estimate = "amce",
  ), feature == "Political Experience"), 
  xlab = NULL, feature_headers = FALSE, vline = 0, xlim = c(-0.21, 0.21), size = 2
) + 
  ggtitle(NULL, "Full Sample AMCEs") + 
  scale_colour_manual("Feature", limits = "Political Experience", values = "black") +
  theme(
  	legend.position = "none",
  	panel.border = element_blank(),
  	axis.line.x = element_blank(),
	axis.line.y = element_blank()
  )

b <- plot(
  subset(cj(
   tkr, 
   winner ~ feature_sex + feature_experience + feature_marital + feature_job + feature_children + feature_age,
   id = ~ responseid,
   estimate = "mm",
  ), feature == "Political Experience"),
  xlab = NULL, feature_headers = FALSE, vline = 0.5, xlim = c(0.29,0.71), size = 2
) + 
  ggtitle(NULL, "Full Sample MMs") + 
  scale_colour_manual("Feature", limits = "Political Experience", values = "black") +
  theme(
   	legend.position = "none",
   	panel.border = element_blank(),
   	axis.line.x = element_blank(),
	axis.line.y = element_blank()
  )

c <- plot(
  subset(cj(
   tkr, 
   winner ~ feature_sex + feature_experience + feature_marital + feature_job + feature_children + feature_age,
   id = ~ responseid,
   estimate = "amce",
   by = ~ PartyID
  ), feature == "Political Experience"), 
  xlab = NULL, feature_headers = FALSE, vline = 0, group = "PartyID", xlim = c(-0.21, 0.21), size = 2
) + 
 annotate("text", y = 1.65, x = -0.04, label = "Republicans", size = 3) + 
 annotate("text", y = 1.3, x = 0.05, label = "Democrats", size = 3) + 
 ggtitle(NULL, "Subgroup AMCEs") + 
 scale_colour_manual(values=rep("black", 2)) +
 aes(shape = PartyID) + 
 scale_shape_manual("PartyID", limits = c("Democrat", "Republican"), values = c(15,17)) +
 theme(
   legend.position = "none",
   panel.border = element_blank(),
   axis.line.x = element_blank(),
   axis.line.y = element_blank()
 )
